
\documentclass[10pt,a4paper,sans]{moderncv}
\usepackage[utf8]{inputenc} 
\moderncvtheme[green]{classic}
\usepackage[scale=0.8]{geometry}
\usepackage{url}
\setlength{\hintscolumnwidth}{1.5cm}
\AtBeginDocument{\recomputelengths}
\firstname{Publications}
\familyname{}
\title{S\'everin Lemaignan}
\begin{document}
\maketitle
\emph{h-index: 14} -- \emph{Citations: 861} (source: Google Scholar, checked on 10/12/2016)

\vspace{1em}\section{International peer-reviewed journals}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Warnier, M., Sisbot, E.A., Clodic, A., Alami, R. \\ \textbf{Artificial Cognition for Social Human-Robot Interaction: An Implementation} \\ \textit{Artificial Intelligence} 2016. DOI:~\texttt{10.1016/j.artint.2016.07.002}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Jacq, A., Hood, D., Garcia, F., Paiva, A., Dillenbourg, P. \\ \textbf{Learning by Teaching a Robot: The Case of Handwriting} \\ \textit{IEEE Robotics and Automation Magazine} 2016. DOI:~\texttt{10.1109/MRA.2016.2546700}.}
\vspace{0.2em}\cvlistitem{Dillenbourg, P., Lemaignan, S., Sangin, M., Nova, N., Molinari, G. \\ \textbf{The Symmetry of Partner Modelling} \\ \textit{Intl. J. of Computer-Supported Collaborative Learning} 2016. DOI:~\texttt{10.1007/s11412-016-9235-5}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S. \\ \textbf{Grounding the Interaction: Knowledge Management for Interactive Robots [dissertation abstract]} \\ \textit{Künstliche Intelligenz} 2013. DOI:~\texttt{10.1007/s13218-013-0246-3}.}
\vspace{0.2em}\cvlistitem{Lallée, S., Pattacini, U., Lemaignan, S., Lenz, A., Melhuish, C., Natale, L., Skachek, S., Hamann, K., Steinwender, J., Sisbot, E.A., Metta, G., Pipe, T., Alami, W., Warnier, M., Guitton, J., Warneken, F., Dominey, P.F. \\ \textbf{Towards a Platform-Independent Cooperative Human-Robot Interaction System: III. An Architecture for Learning and Executing Actions and Shared Plans} \\ \textit{IEEE Transactions on Autonomous Mental Development} 2012. DOI:~\texttt{10.1109/TAMD.2012.2199754}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Ros, R., Sisbot, E. A., Alami, R., Beetz M. \\ \textbf{Grounding the Interaction: Anchoring Situated Discourse in Everyday Human-Robot Interaction} \\ \textit{International Journal of Social Robotics} 2011. DOI:~\texttt{10.1007/s12369-011-0123-x}.}
\vspace{1em}\section{International peer-reviewed conference articles (6-8 pages)}
\vspace{0.2em}\cvlistitem{Özgür, A., Lemaignan, S., Johal, W., Beltran, M., Briod, M., Pereyre, L., Mondada, F., Dillenbourg, P. \\ \textbf{Cellulo: Versatile Handheld Robots for Education} \\ \textit{HRI} 2017. to appear.}
\vspace{0.2em}\cvlistitem{Kennedy, J., Lemaignan, S., Montassier, C., Lavalade, P., Irfan, B., Papadopoulos, F., Senft, E., Belpaeme, T. \\ \textbf{Child Speech Recognition in Human-Robot Interaction: Evaluations and Recommendations} \\ \textit{HRI} 2017. to appear.}
\vspace{0.2em}\cvlistitem{Chandra, S., Alves-Oliveira, P., Lemaignan, S., Sequeira, P., Paiva, A., Dillenbourg, P. \\ \textbf{Children's Peer Assessment and Self-disclosure in the Presence of an Educational Robot} \\ \textit{RoMAN} 2016. DOI:~\texttt{10.1109/ROMAN.2016.7745170}.}
\vspace{0.2em}\cvlistitem{Hostettler, L., Özgür, A., Lemaignan, S., Dillenbourg, P., Mondada, F. \\ \textbf{Real-Time High-Accuracy 2D Localization with Structured Patterns} \\ \textit{ICRA} 2016. DOI:~\texttt{10.1109/ICRA.2016.7487653}.}
\vspace{0.2em}\cvlistitem{Baxter, P., Kennedy, J., Senft E., Lemaignan, S., Belpaeme, T. \\ \textbf{From Characterising Three Years of HRI to Methodology and Reporting Recommendations} \\ \textit{alt.HRI} 2016. DOI:~\texttt{10.1109/HRI.2016.7451777}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Garcia, F., Jacq, A., Dillenbourg, P. \\ \textbf{From Real-time Attention Assessment to “With-me-ness” in Human-Robot Interaction} \\ \textit{HRI} 2016. DOI:~\texttt{10.1109/HRI.2016.7451747}.}
\vspace{0.2em}\cvlistitem{Jacq, A., Lemaignan, S., Garcia, F., Dillenbourg, P., Paiva, A. \\ \textbf{Building Successful Long Child-Robot Interactions in a Learning Context} \\ \textit{HRI} 2016. DOI:~\texttt{10.1109/HRI.2016.7451758}.}
\vspace{0.2em}\cvlistitem{Baxter, P., Ashurst, E., Kennedy, J., Senft, E., Lemaignan, S., Belpaeme, T. \\ \textbf{The Wider Supportive Role of Social Robots in the Classroom for Teachers} \\ \textit{WONDER Workshop - ICSR} 2015.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Fink, J., Mondada, F., Dillenbourg, P. \\ \textbf{You're Doing It Wrong! Studying Unexpected Behaviors in Child-Robot Interaction} \\ \textit{ICSR} 2015. DOI:~\texttt{10.1007/978-3-319-25554-5\_39}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Hosseini, A., Dillenbourg, P. \\ \textbf{pyRobots: a Toolset for Robot Executive Control} \\ \textit{IROS} 2015. DOI:~\texttt{10.1109/IROS.2015.7353769}.}
\vspace{0.2em}\cvlistitem{Karim, M. E., Lemaignan, S., Mondada, F. \\ \textbf{A Review: Can Robots Reshape K-12 STEM Education?} \\ \textit{ARSO} 2015.}
\vspace{0.2em}\cvlistitem{Chandra, S., Alves-Oliveira, P., Lemaignan, S., Sequeira, P., Paiva, A., Dillenbourg, P. \\ \textbf{Can a Child Feel Responsible for Another in the Presence of a Robot in a Collaborative Learning Activity?} \\ \textit{RoMAN} 2015. DOI:~\texttt{10.1109/ROMAN.2015.7333678}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Dillenbourg, P. \\ \textbf{Mutual Modelling in Robotics: Inspirations for the Next Steps} \\ \textit{HRI} 2015. DOI:~\texttt{10.1145/2696454.2696493}.}
\vspace{0.2em}\cvlistitem{Hood, D., Lemaignan, S., Dillenbourg, P. \\ \textbf{When Children Teach a Robot to Write: An Autonomous Teachable Humanoid Which Uses Simulated Handwriting} \\ \textit{HRI} 2015. DOI:~\texttt{10.1145/2696454.2696479}.}
\vspace{0.2em}\cvlistitem{Fink, J., Rétornaz, P., Vaussard, F., Wille, F., Franinović, K., Berthoud, A., Lemaignan, S., Dillenbourg, P., Mondada, F. \\ \textbf{Which Robot Behavior Can Motivate Children to Tidy up Their Toys? Design and Evaluation of “Ranger”} \\ \textit{HRI} 2014. DOI:~\texttt{10.1145/2559636.2559659}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S.,  Hanheide, M., Karg, M., Khambhaita, H., Kunze, L., Lier, F., Lütkebohle, I., Milliez, G. \\ \textbf{Simulation and HRI - Recent Perspectives with the MORSE Simulator} \\ \textit{SIMPAR} 2014. DOI:~\texttt{10.1007/978-3-319-11900-7\_2}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Fink, J., Dillenbourg, P., Braboszcz, C. \\ \textbf{The Cognitive Correlates of Anthropomorphism} \\ \textit{Workshop A bridge between Robotics and Neuroscience - HRI} 2014.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Alami, R. \\ \textbf{Explicit Knowledge and the Deliberative Layer: Lessons Learned} \\ \textit{IROS} 2013. DOI:~\texttt{10.1109/IROS.2013.6697182}.}
\vspace{0.2em}\cvlistitem{Echeverria, G., Lemaignan, S., Degroote, A., Lacroix, S., Karg, M., Koch, P., Lesire, C., Stinckwich, S. \\ \textbf{Simulating complex robotic scenarios with MORSE} \\ \textit{SIMPAR} 2012. DOI:~\texttt{10.1007/978-3-642-34327-8\_20}.}
\vspace{0.2em}\cvlistitem{Warnier, M., Guitton, J., Lemaignan, S., Alami, R. \\ \textbf{When the Robot Puts Itself in Your Shoes. Managing and Exploiting Human and Robot Beliefs} \\ \textit{RoMAN} 2012. DOI:~\texttt{10.1109/ROMAN.2012.6343872}.}
\vspace{0.2em}\cvlistitem{Alami, R., Warnier, M., Guitton, J., Lemaignan, S., Sisbot, E. A. \\ \textbf{When the robot considers the human...} \\ \textit{ISRR} 2011.}
\vspace{0.2em}\cvlistitem{Lallée, S., Pattacini, U., Boucher, J.D., Lemaignan, S., Lenz, A., Melhuish, C., Natale, L., Skachek, S., Hamann, K., Steinwender, J., Sisbot, E.A., Metta, G., Alami, R., Warnier, M., Guitton, J., Warneken, F., Dominey, P.F. \\ \textbf{Towards a Platform-Independent Cooperative Human-Robot Interaction System: II. Perception, Execution and Imitation of Goal Directed Actions} \\ \textit{IROS} 2011. DOI:~\texttt{10.1109/IROS.2011.6094744}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Ros, R., Alami, R., Beetz, M. \\ \textbf{What are you talking about? Grounding dialogue in a perspective-aware robotic architecture} \\ \textit{RoMAN} 2011. DOI:~\texttt{10.1109/ROMAN.2011.6005249}.}
\vspace{0.2em}\cvlistitem{Echeverria, G., Lassabe, N., Degroote, A., Lemaignan, S. \\ \textbf{Modular Open Robots Simulation Engine: MORSE} \\ \textit{ICRA} 2011. DOI:~\texttt{10.1109/ICRA.2011.5980252}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Ros, R., Mösenlechner, L., Alami, R., Beetz, M. \\ \textbf{ORO, a Knowledge Management Module for Cognitive Architectures in Robotics} \\ \textit{IROS} 2010. DOI:~\texttt{10.1109/IROS.2010.5649547}.}
\vspace{0.2em}\cvlistitem{Ros, R., Lemaignan, S., Sisbot, E. A., Alami, R., Steinwender, J., Hamann, K., Warneken, F. \\ \textbf{Which One? Grounding the Referent Based on Efficient Human-Robot Interaction} \\ \textit{RoMAN} 2010. DOI:~\texttt{10.1109/ROMAN.2010.5598719}.}
\vspace{0.2em}\cvlistitem{Lallée, S., Lemaignan, S., Lenz, A., Melhuish, C., Natale, L., Skachek, S., van Der Zant, T., Warneken, F., Dominey, P.F. \\ \textbf{Towards a Platform-Independent Cooperative Human-Robot Interaction System: I. Perception} \\ \textit{IROS} 2010. DOI:~\texttt{10.1109/IROS.2010.5652697}.}
\vspace{0.2em}\cvlistitem{Mallet, A., Pasteur, C., Herrb, M., Lemaignan, S., Ingrand, F. \\ \textbf{GenoM3: Building middleware-independent robotic components} \\ \textit{ICRA} 2010. DOI:~\texttt{10.1109/ROBOT.2010.5509539}.}
\vspace{0.2em}\cvlistitem{Mehani, O., Benenson, R., Lemaignan, S., Ernst, T. \\ \textbf{Networking Needs and Solutions for Road Vehicles at Imara} \\ \textit{ITST} 2007. DOI:~\texttt{10.1109/ITST.2007.4295894}.}
\vspace{0.2em}\cvlistitem{Stinckwich, S., Lemaignan, S., Saidani, S. \\ \textbf{SqueakBot: a Pedagogical Robotic Platform} \\ \textit{C5 Conference} 2007. DOI:~\texttt{10.1109/C5.2007.28}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Siadat, A., Dantan, J.Y., Semenenko, A. \\ \textbf{MASON: A proposal for an ontology of manufacturing domain} \\ \textit{IEEE Workshop on Distributed Intelligent Systems (DIS)} 2006. DOI:~\texttt{10.1109/DIS.2006.48}.}

\vspace{1em}\section{Short peer-reviewed publications}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Kennedy, J., Baxter, P., Belpaeme, T. \\ \textbf{Towards Machine-Learnable Child-Robot Interactions: the PInSoRo Dataset} \\ \textit{RoMAN - Workshop on Long-term Child-robot Interaction} 2016.}
\vspace{0.2em}\cvlistitem{Kennedy, J., Lemaignan, S., Belpaeme, T. \\ \textbf{The Cautious Attitude of Teachers Towards Social Robots in Schools} \\ \textit{RoMAN - Workshop on Robots for Learning} 2016.}
\vspace{0.2em}\cvlistitem{Senft, E., Baxter, P., Kennedy, J., Lemaignan, S., Belpaeme, T. \\ \textbf{Providing a Robot with Learning Abilities Improves its Perception by Users} \\ \textit{HRI} 2016. DOI:~\texttt{10.1109/HRI.2016.7451832}.}
\vspace{0.2em}\cvlistitem{Baxter, P., Lemaignan, S., Trafton, G. \\ \textbf{Workshop on Cognitive Architectures for Social Human-Robot Interaction} \\ \textit{HRI} 2016. DOI:~\texttt{10.1109/HRI.2016.7451865}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Alami, R. \\ \textbf{A Few AI Challenges Raised while Developing an Architecture for Human-Robot Cooperative Task Achievement} \\ \textit{AAAI 2014 Fall Symposium Series - Artificial Intelligence and Human-Robot Interaction} 2014.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Fink, J., Dillenbourg, P. \\ \textbf{The Dynamics of Anthropomorphism in Robotics} \\ \textit{HRI} 2014. DOI:~\texttt{10.1145/2559636.2559814}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Echeverria, G., Karg, M., Mainprice, M., Kirsch, A., Alami, R. \\ \textbf{Human-Robot Interaction in the MORSE Simulator} \\ \textit{HRI} 2012. DOI:~\texttt{10.1145/2157689.2157745}.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Ros, R., Alami, R. \\ \textbf{Dialogue in situated environments: A symbolic approach to perspective-aware grounding, clarification and reasoning for robots} \\ \textit{Workshop Grounding Human-Robot Dialog for Spatial Tasks - RSS} 2011.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Sisbot, E. A., Alami, R. \\ \textbf{Anchoring interaction through symbolic knowledge} \\ \textit{HRI Pioneers - HRI} 2011. ISBN:~978-0-557-79488-1.}
\vspace{0.2em}\cvlistitem{Ros, R., Sisbot, E. A., Lemaignan, S., Pandey, A. K., Alami, R. \\ \textbf{Robot, tell me what you know about...?: Expressing robot's knowledge through interaction} \\ \textit{ICAIR} 2010.}

\vspace{1em}\section{Book chapters}
\vspace{0.2em}\cvlistitem{Mondada, F., Fink, J., Lemaignan, S., Mansolino, D., Wille, F., Franinović, K. \\ \textbf{Ranger, an Example of Integration of Robotics into the Home Ecosystem} \\ 2015.}
\vspace{0.2em}\cvlistitem{Lemaignan, S., Alami, R., Pandey, A. K., Warnier, M., Guitton, J. \\ \textbf{Towards Grounding Human-Robot Interaction} \\ 2012.}

\vspace{1em}\section{Dissertation}
\vspace{0.2em}\cvlistitem{Lemaignan, S. \\ \textbf{Grounding the Interaction: Knowledge Management for Interactive Robots} \\ \textit{CNRS - LAAS | TU München - Intelligent Autonomous Systems lab} 2012.}


\end{document}

